Meta-analysis

### 2019-09-14 05_MetaAnalysis.Rmd
Use barplot in place of table for dose/ha tebu ai

Tebuconazole and propiconazole might be able to be pooled as a 'triazole' fungicide treatment. 
Amistar Xtra is a combination of azoxystrobin and cyproconazole.
Perhaps Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however they contain differing dose ratio (inverted).

@@

Preliminary analysis of fungicides show there is a difference the effect of fungicide in proportion of yield gained

### Fungicide Doses
All trials that used tebuconazole used approximately the same dose.
Dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare.

>>>>

Tebuconazole and propiconazole might be able to be pooled as a 'triazole' fungicide treatment. 
Amistar Xtra is a combination of azoxystrobin and cyproconazole.
Custodia is a combination of tebuconazole and azoxystrobin.
Perhaps Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however they contain differing dose ratios (inverted).

@@

Preliminary analysis of fungicides show there is a difference the effect of fungicide in proportion of yield saved.

### Fungicide Doses

All trials that used tebuconazole used approximately the same dose.
Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
